Tabsets

### 2024-07-09 app_par.qmd
tabsets

```{r, echo=F,message=FALSE,warning=FALSE}
ManifoldDestiny::wasmconload()
library(ManifoldDestiny)
#library(ManifoldDestinyWASMP)
#library(ManifoldDestinyWASMD)
#library(dplyr)
#library(ggplot2)
#library(dplyr)
#library(combinat)
#library(htmltools)
#library(ggplot2)
#library(broom)
#library(combinat)
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
mda <- app0[[2]]
asrp <- selreport(app0)
asop <- seloutput(asrp)
```

>>>>

```{r, echo=F,message=FALSE,warning=FALSE}
ManifoldDestiny::wasmconload()
library(ManifoldDestiny)
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
mda <- app0[[2]]
asrp <- selreport(app0)
asop <- seloutput(asrp)
```

### 2024-07-09 tabsets.qmd
tabsets

---
title: "Tabsets"
format: 
  html:
    page-layout: article
#filters:
#  - webr
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
#    footer: <https://lotariohw26.github.io/ManifoldDestiny/>
#execute: 
#  cache: false
# app_par.qmd
bibliography: man_bib.bib
---

@@

```{r}
knitr::knit_exit()
```

```{r, echo=F, message=F, warning=F}
ManifoldDestiny::wasmconload()
modlat <- eqpar$meql
md <- ManifoldDestinyWASMD::metad
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
```

::: {.callout-caution collapse="true"}
## `r md$tabhead[1]`
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_n_out
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## `r md$tabhead[2]`
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_ex1_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## `r md$tabhead[3]`
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_ex2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## `r md$tabhead[4]`
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_ex3_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## Application 0 
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_0_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## Application 1 
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_1_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## Application 2 
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::
::: {.callout-caution collapse="true"}
## Application 3 
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::
::: {.callout-caution collapse="true"}
## Application 4 
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::
::: {.callout-caution collapse="true"}
## Application 5 
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

>>>>

---
title: ""
---

@@

```{r, echo=F,message=FALSE,warning=FALSE}
ManifoldDestiny::wasmconload()
library(ManifoldDestiny)
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
mda <- app0[[2]]
asrp <- selreport(app0)
asop <- seloutput(asrp)
```

::: {.callout-caution collapse="true"}
## {{< var tabh.h1 >}}
```{r, echo=FALSE, results='asis',warning=F}
#app_a_out <- app_0_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var tabh.h2 >}}
```{r, echo=FALSE, results='asis',warning=F}
#app_a_out <- app_1_out 
#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
#text <- readLines(app1_fil)
#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var tabh.h3 >}}
```{r, echo=FALSE, results='asis',warning=F}
#app_a_out <- app_2_out 
#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
#text <- readLines(app1_fil)
#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var sec6.un1 >}}
```{r, echo=FALSE, results='asis',warning=F}
#app_a_out <- app_2_out 
#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
#text <- readLines(app1_fil)
#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var sec6.un2 >}}
```{r, echo=FALSE, results='asis',warning=F}
#app_a_out <- app_2_out 
#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
#text <- readLines(app1_fil)
#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var sec6.un3 >}}
```{r, echo=FALSE, results='asis',warning=F}
#app_a_out <- app_2_out 
#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
#text <- readLines(app1_fil)
#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var sec6.un4 >}}
```{r, echo=FALSE, results='asis',warning=F}
#app_a_out <- app_2_out 
#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
#text <- readLines(app1_fil)
#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

```{r, echo=F}
knitr::knit_exit()
```
